Optimizing the power of adaptive seamless designs using Bayesian Optimization

### 2020-10-21 main.tex
anything?

\begin{figure}[htb]
\centering
  \begin{minipage}{0.64\textwidth}
    \centering
    \includegraphics[width=\linewidth]{generated/figures/plot_opt_path_5000.pdf}%
    \captionof{figure}{Opt Path}
    \label{fig:plot_opt_path_5000}
  \end{minipage}\hspace{0.01\textwidth}%
  \begin{minipage}{0.35\textwidth}
    \centering
    \includegraphics[width=\linewidth]{generated/figures/plot_boxplot_valid_y_5000.pdf}%
    \captionof{figure}{Boxplot}
    \label{fig:plot_boxplot_valid_y_5000}
  \end{minipage}
\end{figure}

>>>>

\begin{figure}[htb]
\centering
  \begin{minipage}{0.62\textwidth}
    \centering
    \includegraphics[width=\linewidth]{generated/figures/plot_opt_path_5000.pdf}%
    \captionof{figure}{Optimization progress for \emph{MBO} in each stochastic repetition in comparison to the best found outcome in the grid search on effect set \emph{paper} and $n_{\text{treat}} = 2000$.}
    \label{fig:plot_opt_path_5000}
  \end{minipage}\hspace{0.02\textwidth}%
  \begin{minipage}{0.35\textwidth}
    \centering
    \includegraphics[width=\linewidth]{generated/figures/plot_boxplot_valid_y_5000.pdf}%
    \captionof{figure}{Validated performance of all optimization strategies on effect set \emph{paper} and $n_treat = 2000$ with 100 stochastic repititions and different values for \texttt{nsim}}
    \label{fig:plot_boxplot_valid_y_5000}
  \end{minipage}
\end{figure}
